---
title: "Assignment"
author: 'Pouya:Shruthi: Adarsh'
date: "July 12, 2016"
output: word_document
---
#Assignment  :: :: :: Adarsh :: Pouya :: Shruthy :: :: ::

Question: TO compare the Tweets about NarendraModi and Rahulgandhi and the frequent used words in those posts.

Connecting R and Tweets with personally generated tokens of key, secret key

```{r}
tw_token = "446728348-5HZVSTuJohw7SmMdyUsHFAlEEt29ex1y3Ysez587"
tw_token_secret = "DWLkZfAdj4dTrZQzEwV3BMl8ePjEPalJa8dQWjwZnbdJ1"
tw_consumer_key = "WMfGLAtO1AGA13c4NFRNp0pHZ"
tw_consumer_secret ="PMZnkAp9qVe30ZWNw0jzXJXQqiLC2QJLAxz9wpQ0cv7FzIrzac"
```
Setting up R to get tokens and key
```{r}
library(twitteR)
setup_twitter_oauth(tw_consumer_key,tw_consumer_secret,tw_token,tw_token_secret)
```
Creation of separate variable for Rahulgandhi, Modi
```{r}
rahul = searchTwitter("rahulgandhi", n=1000)
modi=searchTwitter("modi",n=1000)
```
Creation of Separate Dataframes
```{r}
rahul = plyr::ldply(rahul, as.data.frame)
modi=plyr::ldply(modi, as.data.frame)
```
Installing packages
```{r}
##install.packages("RTextTools")
library(RTextTools)
```
Changing the Format to Matrix
```{r}
dtmr = create_matrix(rahul$text, stemWords = F)
dtmm = create_matrix(modi$text, stemWords = F)
```

```{r}
library(corpustools)
```
Corpus Comparision
```{r}
cmp = corpora.compare(dtmr, dtmm)
```

```{r}
head(cmp)
```
```{r}
cmp=arrange(cmp,-chi)
```
```{r}
View(cmp)
```

```{r}
library(corpustools)
cmp = corpora.compare(dtmm, dtmr)
cmp  = arrange(cmp, -chi)
```

```{r}
View(cmp)
```



Wordplot comparison on all words that people used about Modi and Rahul
```{r}
with(head(cmp, 100),
     plotWords(x=log(over), words = term, wordfreq = chi, random.y = T))
```

Removing the words Modi and Rahul as they occur the most
```{r}
newmatrix <- cmp[3:dim(cmp)[1],]
```


Word Plot after removing the words Modi and Rahul
```{r}
with(head(newmatrix, 100),
     plotWords(x=log(over), words = term, wordfreq = chi, random.y = T))
```

```{r}
cmp  = arrange(cmp, -chi)
```

```{r}
View(newmatrix)
```

```{r}
plot(x=cmp$term, y=cmp$over, type="l")
```

```{r}
m = lda.fit(dtmm, K=10)
terms(m,10)
```

```{r}
r = lda.fit(dtmr, K=10)
terms(r,10)
```

```{r}
##install.packages("devtools")
devtools::install_github("cpsievert/LDAvis")
library(LDAvis)
```

```{r}
json_modi=ldavis_json(m,dtmm)
serVis(json_modi)
```

```{r}
json_rahul=ldavis_json(r,dtmr)
serVis(json_rahul)
```




The Tool is really powerful in the analysis. But the knowledge about the existance of packages are the key to do it. So there could be something to make people know about the package within the studio itself, rather than googling about the existance.
